Spin canonical divisors of log stacky curves

### 2015-06-27 stacky_write_up/spin_cring.tex
minor edits to intro to section 3

\section{Background}
\label{sec:background}
Look at Spencer-Kodaira \cite{kodaira:complex-manifolds}.
Include the following:
\begin{enumerate}
	\item Possibly include some of the following notation, it it isn't dealt with well in the background.

@@

\section{Inductive Lemmata}
\label{sec:induction}
First we present the general inductive Lemmata that will be applied
for all genera. We offer various inductive Lemmata that will allow
us to add fractional point $\frac{\alpha}{\beta}P$ to a $\BQ$
 divisor $D$ of $X$ and describe the new generators and relations
of $R_{D + P}$ not in $R_D$. Next, we provide a method specific to
the case of stacky canonical divisors, which
under certain conditions allows us to transfer information about
the generators and relations of the half canonical ring of a stacky
curve $\sx$' with signature $(g; e_1', \ldots, e_\tau'; 0)$ to a
stacky curve $\sx$ with signature $(g; e_1, \ldots, e_\tau; 0)$
where each $e_i\in \{e_i', e_i' + 2\}$.

@@

\ssec{Inductive Lemmata: Adding Points}
\label{ssec:add_pts}
In this section, we prove various inductive statements under the following setup:
Let $\halfcan'$ be $\BQ$-divisor of $X$ (and often a log half-canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbb{N}$ and certain saturation conditions. Let $\halfcan=\halfcan'+P$ for some $P$ possibly in the support of $\halfcan$.  Then we will explicitly describe elements that generate $R_\halfcan$ over $\halfcan$' and initial terms of relations that generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Gr\"{o}bner Basis).

@@

\ssec{Raising Stabilizer Orders}
\label{ssec:ram_orders}
In this subsection, we aim to prove Lemma
~\ref{lem:raise-stacky-order}, whose proof is almost identical to that of \cite[Theorem 8.5.7]{vzb:stacky}. In many cases, Lemma ~\ref{lem:raise-stacky-order} implies that if the main result, Theorem 
~\ref{thm:main}, holds for a curve with signature
$(g;e_1', \ldots, e_k', e_{k+1}' \ldots, e_r';\delta),$ with $e_{k+1}' = \cdots = e_r',$ then Theorem ~\ref{thm:main} also holds for a curve with
signature $(g; e_1', \ldots, e_k',e_{k+1}'+2,\ldots, e_r'+2; \delta).$ In order to state Lemma
~\ref{lem:raise-stacky-order}, we will need to define a certain notion of admissibility in Definition ~\ref{defn:admissible}, which is quite similar to \cite[Definition 8.5.1]{vzb:stacky}.

@@

>>>>

\section{Background}
\label{sec:background}
Look at Spencer-Kodaira \cite{kodaira:complex-manifolds}.
Include the following:
\begin{enumerate}
	\item Include explanation of Kodaira spencer, and use \cite[Lemma 10.2.1]{vzb:stacky} to obtain the desired translation to algebraic geometry.
	\item Possibly include some of the following notation, it it isn't dealt with well in the background.

@@

\section{Inductive Lemmata}
\label{sec:induction}
First we present several lemmata which play a crucial role in the inductive step of the proof of the main theorem, Theorem ~\ref{thm:main}. In Subsection ~\ref{ssec:add-points} we prove Lemma ~\ref{lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3} which describe the generators and relations of $R_{D + \frac{\alpha}{\beta}P},$ given those in $R_D,$ where $X$ is a curve, $D \in \di X \otimes \BQ$ and  $\frac{\alpha}{\beta} \in \BQ.$ Next, in Subsection ~\ref{ssec:raise-orders}, we prove Lemma ~\ref{lem:raise-stacky-order}, which the generators and relations of the log spin canonical ring curve with signature $(g; e_1', \ldots, e_\tau'; 0)$ to that of the log spin canonical ring of a curve with a certain subset of the $e_i'$ incremented by $2$. While Lemma ~\ref{lem:sat-1} may be applied in a fairly general context, Lemma ~\ref{lem:raise-stacky-orders} is more specific to half-canonical divisors, although even Lemma ~\ref{lem:raise-stacky-orders} has certain generalizations, as noted in Remark ~\ref{rem:raise-fractional-orders}

@@

\ssec{Inductive Lemmata: Adding Points}
\label{ssec:add-points}
In this section, we prove various inductive statements under the following setup:
Let $\halfcan'$ be $\BQ$-divisor of $X$ (and often a log half-canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbb{N}$ and certain saturation conditions. Let $\halfcan=\halfcan'+P$ for some $P$ possibly in the support of $\halfcan$.  Then we will explicitly describe elements that generate $R_\halfcan$ over $\halfcan$' and initial terms of relations that generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Gr\"{o}bner Basis).

@@

\ssec{Raising Stabilizer Orders}
\label{ssec:raise-orders}
In this subsection, we aim to prove Lemma
~\ref{lem:raise-stacky-order}, whose proof is almost identical to that of \cite[Theorem 8.5.7]{vzb:stacky}. In many cases, Lemma ~\ref{lem:raise-stacky-order} implies that if the main result, Theorem 
~\ref{thm:main}, holds for a curve with signature
$(g;e_1', \ldots, e_k', e_{k+1}' \ldots, e_r';\delta),$ with $e_{k+1}' = \cdots = e_r',$ then Theorem ~\ref{thm:main} also holds for a curve with
signature $(g; e_1', \ldots, e_k',e_{k+1}'+2,\ldots, e_r'+2; \delta).$ In order to state Lemma
~\ref{lem:raise-stacky-order}, we will need to define a certain notion of admissibility in Definition ~\ref{defn:admissible}, which is quite similar to \cite[Definition 8.5.1]{vzb:stacky}.

@@

\begin{rem}
\label{rem:raise-fractional-order}
It is no coincidence that the proofs of Lemma ~\ref{lem:raise-stacky-orders} and \cite[Theorem 8.5.7]{vzb:stacky} are almost identical. In fact, the proofs of both results can easily be generalized generalized to the case of fractional canonical divisors, that is $L \in \di X$ with $nL \sim K$, for any $n \in \BZ_{\geq 1}$.
\end{rem}
